
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome5} % For icons
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
    \name{Deepak Kumar Prasad}
    \address{
    \faIcon{phone-square-alt} +91 8861 327919 \;|\;
    \faIcon{mobile-alt} +1 (707) 733-3727
    }
    \address{
        \faIcon{map-marker-alt} Bangalore, India (Open to relocation)
    }
    \address{
        \faIcon{envelope} \href{mailto:deepak.prasad.ai@gmail.com}{deepak.prasad.ai@gmail.com} \;|\;
        \faIcon{linkedin} \href{https://www.linkedin.com/in/dpkpr1}{linkedin.com/in/dpkpr1} \;|\;
        \faIcon{link} \href{https://deepak-prasad.streamlit.app/}{deepak-prasad.streamlit.app}
    }

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}

    {
       Technical leader with 9+ years architecting large-scale supply chain platforms serving 150+ global clients. Proven track record in performance engineering (50\% runtime reduction, 30\% memory optimization), solver integrations, and leading 10+ developer teams across Python, microservices, and distributed systems. Seeking Senior/Lead Software Engineer or Technical Architect roles.
    }

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
% Main company entry with total tenure
\textbf{o9 Solutions, Bangalore} \hfill Feb 2019 -- Present \\
% Nested job titles showing progression. Use \textit for visual distinction.
\textit{Senior Application Architect \hfill Apr 2025 -- Present} \\
\textit{Application Architect \hfill Apr 2021 -- Apr 2025} \\
\textit{Senior Software Engineer \hfill Aug 2019 -- Apr 2021} \\
\textit{Python Developer (Contract) \hfill Feb 2019 -- Aug 2019}

% \textbf{Senior Application Architect} \hfill Feb 2019 -- Present \\
% o9 Solutions, Bangalore \\
\begin{itemize}
    \item \textbf{Led Supply Planning engineering team} (10+ developers), driving development and maintenance of production modules (TLB, MRP, IOP, core SP) across 50+ client-specific customizations while maintaining high availability for 150+ global clients.
    
    \item \textbf{Re-engineered critical Supply Planning components} to enable advanced parameterization and performance optimization, achieving \textbf{50\% reduction in batch computation time} and \textbf{30\% decrease in memory usage} across multiple production environments.
    
    \item \textbf{Architected and integrated 6+ third-party solvers} with o9 platform, including Samsung NSR solver using Boost serialization and Parquet-based data exchange, improving reliability and deployment scalability.
    
    \item \textbf{Designed foundational Demand Netting and Order Promising plugins}—mission-critical modules now serving 150+ clients globally. Enhanced plugins with advanced configuration and monitoring capabilities for enterprise-scale deployments.
    
    \item \textbf{Engineered productivity suite} (7 tools: Tenant Extractor, Builder, Performance Analyzer, Test Recorder/Runner, Rule Creator, Dataset Multiplier) improving consultant productivity by \textbf{25\%}, adopted by 100+ internal teams.
    
    \item \textbf{Managed version control for 30+ plugin variants} enabling modular deployments and customizations without core platform disruption, supporting rapid client onboarding and maintenance cycles.

    \item \textbf{Mentored team members} driving technical skill development and delivering regular workshops on supply planning architecture and optimization techniques.
\end{itemize}
\vspace{1em}
% Primesoft Solutions Inc, Bangalore
\textbf{Primesoft Solutions Inc, Bangalore} \hfill Jun 2016 -- Jul 2018 \\
Associate Engineer \\
\begin{itemize}
    \item \textbf{Architected workflow orchestration microservice} leveraging Netflix Conductor, customizing the open-source framework for enterprise orchestration requirements and integrating it into production infrastructure.
    \item \textbf{Modernized legacy systems} by integrating 5+ Google APIs and refactoring core codebases, improving system reliability by \textbf{30\%} and reducing technical debt across a large-scale enterprise security platform.
    \item \textbf{Built Attendance \& Visitor Management systems} (Android), automating check-ins and visitor tracking—reducing manual overhead by \textbf{70\%} with actionable facility analytics.
\end{itemize}

\end{rSection} 
\vspace{1em}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf Bachelor of Engineering in Computer Science} % Degree
  {(SJCE, Mysore)} % Institution
  \hfill {August 2012 -- May 2016} % Date

  % {Relevant Coursework: }{C, C++, Java, Pattern Recognition, Cloud Computing, Big Data, Machine Learning, System Design \& Architecture, Statistics Modelling }

  % % \section*{Projects}
  % {
  %   \begin{itemize}
  %     \item \textbf{Gender Recognition based on Palm-print for Pattern Recognition} – Captured palm-print images and used dimensional features for gender classification using MATLAB.
  %     \item \textbf{Congestion Control for Computer Network} – Implemented priority-based load-shedding to control congestion in networks using C.
  %     \item \textbf{Web Tutorial} – Developed a text and video-based e-learning website using HTML, CSS, and JavaScript.
  %   \end{itemize}
  % }

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\textbf{Technical Skills}
\vspace{0.5em}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{15cm} }
    Languages & Python, Java, C, C++, SQL \\
    Frameworks \& Libraries & FastAPI, ReactJS, Angular, Streamlit, Boost (C++) \\
    Data \& Messaging & PostgreSQL, RDBMS, Parquet, ETL Pipelines, Data Serialization \\
    DevOps \& Tools & Docker, Kubernetes, Git, CI/CD, Linux \\
    Architecture & Microservices, Distributed Systems, API Design, Performance Optimization, System Design \\
    Domain & Supply Chain Planning (MRP, Demand Netting, Order Promising), Technical Leadership \\
    Spoken Languages & English, Hindi, Manipuri, Bhojpuri, German \\
\end{tabular}


% \textbf{Soft Skills} 

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{10cm} }
%     & Problem Solving, Debugging \& Troubleshooting, Mentoring \\
% \end{tabular}

% \textbf{Spoken Languages}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{10cm} }
%     Spoken Languages & English, Hindi, Manipuri, Bhojpuri, German \\
% \end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

% \begin{rSection}{PROJECTS}
% \vspace{-1.25em}
%     \item For a detailed list of projects showcasing my technical expertise and impact, please visit: \\
%     \href{https://deepak-prasad.streamlit.app/work}{https://deepak-prasad.streamlit.app/work}
% \end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS}
\vspace{-1.25em}
    \item \textit{Full certification portfolio:} \href{https://deepak-prasad.streamlit.app/certificates}{deepak-prasad.streamlit.app/certificates}
\end{rSection}

\end{document}

